%% start of file `resume.tex'.
%% Copyright 2006-2017 Anish Sheela (aneesh.nl@gmail.com), Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,sans]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[red]{classic}                % idem

\moderncvstyle{classic}
\moderncvcolor{red}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{3cm} %TODO: Adjust						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Anish}
\familyname{A}
%\title{Acquia Certified Drupal Developer}               % optional, remove the line if not wanted
\address{Anugraha, SMN-52, Konchiravila, Manacaud P. O.}{Thiruvananthapuram-695009, Kerala, India}
\mobile{+91-8907509611}                    % optional, remove the line if not wanted
% \phone{+91-471-2459094}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{aneesh.nl@gmail.com}                      % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Freedom is elixir, Freedom is life\\ For people with self-respect,\\ Dependence is worse than death.\\
%\begin{small}
%\textit{- Kumaranasan}
%\end{small}}
%\quote{For detailed online version - anishsheela.com/resume }

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

% TODO: Update section.
\section{Drupal Specific Skills}
\cvline{Certification}{\textbf{Acquia Certified Drupal 8 Foundations Exam - 87.5\%}}
\cvline{Expertise}{
\begin{itemize}
\item Drupal 8
\item Multilingual sites, Entities, REST API design, Drupal Commerce
\item Theming - Bootstrap, Responsive designs, Sass, etc.
\item Custom module development.
\item Deployment, Scaling, Maintenance.
\item Debugging, Coding standards, Best practices, etc.
\end{itemize}
}

\cvline{Community}{
\begin{itemize}
\item \textbf{https://www.drupal.org/u/anish.a}
\item \textbf{https://github.com/anishsheela}
\item Current maintainer of search404, owlcarousel (D8), csv\_txt\_formatter.
\item Ported or contributed on owlcarousel, disable\_messages, etc.
\item Core contributor.
\item \#1 in Malayalam localization.
\item DrupalCon - Drupal Asia 2016
\item DrupalCamp - Pune, Hyderabad, Delhi \& Bangalore
\item FOSSAsia Singapore - Volunteer
\end{itemize}
}

\section{Technical Skills}
\cvline{Operating System}{GNU/Linux, Mainly Debian based distros}
\cvline{Programing Languages}{PHP, Python, C, Ruby}
\cvline{Database}{MySQL}
\cvline{Version Control}{git}
\cvline{Web}{HTML, CSS, Javascript, Bootstrap, Wordpress}
\cvline{Utilities}{GIMP, Libre Office, \LaTeX}
\cvline{Server}{More than 5 years expertise in setting up various application servers.}
%\cvline{Hardware}{Good experience in hardware troubleshooting, advanced networking etc.}
%\cvline{Pursuing}{Ruby on Rails, Linux foundation system admin certification}


\section{My Superpowers}
\cvline{Fast Learner}{I can learn anything easily and in minimum time.}
\cvline{Problem Solver}{I can fix bugs \& issues fast.}
\cvline{Basics}{I know how things work, from the basics.}
\cvline{Social}{A well networked person whom many considers as their first 'goto' block.}
\cvline{Community}{Actively involved in community activities \& projects.}

\section{Work Experience}

\subsection{Axelerant Technologies}
\cvline{URL}{https://www.axelerant.com}
\cvline{Job Title}{Drupal Developer}
\cvline{Duration}{2016 July - Present}
\cvline{Job Description}{Drupal technology expert. I was responsible for the following.
\begin{itemize}
\item Working on Drupal 7 \& 8 projects.
\item Maintaining large scale D7 projects.
\item Architect and develop D8 projects from scratch.
\item Working with self organized agile teams.
\item Handling deployments using docker.
\item Working with testing team for implementation of automated testing (behat).
\item Working on hiring committee \& take decision on new candidates.
\end{itemize}
}

\subsection{Zyxware Technologies Private Limited}
\cvline{URL}{http://www.zyxware.com}
\cvline{Job Title}{Senior Software Engineer}
\cvline{Duration}{2014 August - 2016 July}
\cvline{Job Description}{Drupal technology expert. I was responsible for the following.
\begin{itemize}
\item Working on small to large drupal projects.
\item Domain expert on e-commerce and multilingual websites.
\item Managing servers \& Infrastructure for company as well as clients.
\item Product design and development from scratch.
\item Leading a team of 5 people on drupal community contributions.
\item Working with clients on the role of domain expert.
\item Interviewing and make decision on hiring new candidates.
\end{itemize}
}

\subsection{Hello Infinity Business Solutions Private Limited}
\cvline{URL}{http://www.helloinfinity.com}
\cvline{Job Title}{Co-Founder \& Technical Lead}
\cvline{Duration}{2012 June - 2014 August}
\cvline{Job Description}{We started the company while final year of college. Me as a co-founder \& Technical lead, was responsible for the following.
\begin{itemize}
\item Handling all technology decisions for company.
\item Managing servers \& Infrastructure.
\item Ensure timely closure of projects.
\item Bringing new business to company.
\item Coordinating free software contributions and keeping touch with community.
\end{itemize}
}

\section{Projects}

\cvline{}{\textit{Important projects, reverse chronologically sorted}}

\cvline{}{\textbf{Contract management with workflow} | Drupal 8}
\cvline{Organization}{Axelerant Technologies}
\cvline{Description}{\small Contract management system with workflow and document management. My tasks include
\begin{itemize}
\item Take part in architectural design of the project.
\item Implement the project creation, validation according to requirements
\item Setting up development environments and workflow.
\end{itemize}
}

\cvline{}{\textbf{Medical device advertorial website} | Drupal 8}
\cvline{Organization}{Axelerant Technologies}
\cvline{Description}{\small Website that includes all information on particular medical product. My tasks include
\begin{itemize}
\item Take part in architectural design of the project.
\item Implementing the project backend.
\item Setting up development environments and workflow.
\item Deploying the project in Acquia cloud.
\item Handling client queries and making sure the site is rules complaint.
\end{itemize}
}


\cvline{}{\textbf{Charity website maintenance} | Drupal 7}
\cvline{Organization}{Axelerant Technologies}
\cvline{Description}{\small Maintenance of foreign charity website with millions in donations and worldwide presence. My tasks include
\begin{itemize}
\item Establish formal developer workflow.
\item Setting up development environments.
\item Fix issues raised by client.
\item Development of new features.
\item Refactoring existing codebase.
\item Assistance for automated testing to testing team.
\end{itemize}
}


\cvline{}{\textbf{e-Tendering system for foreign government} | Drupal 7}
\cvline{Organization}{Zyxware Technologies Private Limited}
\cvline{Description}{\small Multilingual e-Tendering system with provision to publish specifications and accept bids. My tasks include
\begin{itemize}
\item Fix major bugs and refactor the code.
\item Add new functionalities, without disturbing existing ones.
\item Fixing all multilingual issues (localization, internationalization).
\item Communicating with client and other stakeholders.
\end{itemize}
}

\cvline{}{\textbf{Event ticket selling platform} | Drupal 7, Drupal Commerce}
\cvline{Organization}{Zyxware Technologies Private Limited}
\cvline{Description}{\small Ticket procuring and selling platform with millions as turnover. My tasks include
\begin{itemize}
\item Designing and implementing anti-price crawling system.
\item Creating custom reports for customer.
\item Mobile website for the same using bootstrap.
\item Bug fixes and Maintenance support.
\end{itemize}
}

\cvline{}{\textbf{Geotagger} | Drupal 7, Entities}
\cvline{Organization}{Zyxware Technologies Private Limited}
\cvline{Description}{\small Mobile application to take photos along with geolocation. Connects to any drupal website using a custom module via REST API. My tasks include
\begin{itemize}
\item Requirement collection and preparation of SRS.
\item Technical design of the mobile \& webapp.
\item Implementation with entities, custom fields, gmaps, REST API, etc.
\item Supporting team on further extension of the system.
\end{itemize}
}

\cvline{}{\textbf{High end audio products information and selling platform} | Drupal 7, Ubercart}
\cvline{Organization}{Zyxware Technologies Private Limited}
\cvline{Description}{\small Producer of high end audio devices. Mainly informational website with cool graphics. My tasks include
\begin{itemize}
\item Convert existing site to responsive design using bootstrap.
\item Refactoring the code to make it maintainable.
\item Additional functionalities requested by client.
\end{itemize}
}

\cvline{}{\textbf{IFFK film festival registration management} | Eventival}
\cvline{Organization}{Kerala Film Academy}
\cvline{Description}{\small Technical consultant to handle registration process, printing \& distribution of badges for around 17,000 delegates in International Film Festival, Kerala.}

\cvline{}{\textbf{FishInGlass cloud based CRM} | PHP, Custom Framework, Python}
\cvline{Organization}{Hello Infinity Business Solutions Private Limited}
\cvline{Description}{\small Top level design of the whole CRM \& Framework. Also done some important modules and interfacing with hardware using python.}

\cvline{}{\textbf{Automation of Cloudamaze webhosting} | WHMCS, WHM/cPanel, Payzippy}
\cvline{Organization}{Hello Infinity Business Solutions Private Limited}
\cvline{Description}{\small Automated the hosting \& domain purchases, billing, etc of Cloudamaze and saved significant maintenance overhead.}

\cvline{}{\textbf{Firewall \& Networking Infrastructure setup} | pfsense, Owncloud, samba}
\cvline{Organization}{Marunadan Malayali}
\cvline{Description}{\small Increased productivity using super fault tolerant Internet connection setup using loadbalancing with pfsense firewall. Upgraded whole computing infrastructure to be easily manageable.}

\section{Community}

\cvline{SMC}{\small Executive committee member of Swatantra Malayalam Computing, which works on Indian language computing area.}
\cvline{FUEL}{\small Part of the expert committee on standardization of Malayalam technical glossary.}
\cvline{GNOME}{\small GNOME commiter (for Malayalam localization) and foundation member.}
\cvline{Mozilla}{\small Active contributor for Malayalam translation of Firefox and Firefox Mobile.}
\cvline{savepoddery}{\small Major role in organizing crowd funding campaign for saving poddery.com.}
\cvline{debian}{\small Debian package maintainer. Maintains few ruby libraries as a part of diaspora packaging.}


\section{Education}
\cventry{2008--2012}{Bachelor of Technology in Computer Science and
Engineering}{Mohandas College of Engineering and Technology}{Thiruvananthapuram}{CGPA \textit{6.8}}
{}
\cventry{2006--2008}{Higher Secondary}{Govt: S.M.V Model Higher Secondary School}{Thiruvananthapuram}{\textit{82\%}}{}
\cventry{2000--2006}{School}{St. Joseph's Higher Secondary School}{Thiruvananthapuram}{\textit{77\%}}{}

\section{Outside of Work}
\cvline{Conferences}{I can be found at many free software related conferences as speaker or otherwise.}
\cvline{Community}{Attending and organizing various community activities.}
\cvline{Travel}{Long distance rides at my motorbike \& other travels.}
\cvline{Rubiks}{Can solve a 3x3 Rubiks cube in one minute \& other variants in reasonable time.}

\section{Personal Information}
\cvline{Date of Birth}{7 April, 1990}
\cvline{Sex}{Male}
\cvline{Blood Group}{A+ve}
\cvline{Languages}{Malayalam(Mother Tongue), English, Hindi (Basic), Tamil (Basic)}
\cvline{Nationality}{Indian}

\end{document}

%% end of file `template_en.tex'.
