%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3}\\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[1][2.5mm]{
    \par\addvspace{#1}
}

% preamble
\firstname{Anish}
\familyname{Anilkumar}
\address{Kerala, India}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{aneesh.nl@gmail.com} & \mobilephonesymbol\enspace +91 9620263587 & \faLinkedin\enspace \href{https://www.linkedin.com/in/anishanil/}{linkedin.com/in/anishanil}
\end{tabularx}
\vspace{-2.0mm}

% left column
\begin{minipage}[t]{0.62\textwidth}
\section{EXPERIENCE}
\experienceentry{Meta}{Fullstack Engineer, Contracted by Alpha Net, SG}{2023 March - 2023 October}{Singapore}

\begin{itemize}
    \item Maintained internal web tools to ensure compliance with privacy standards.
    \item Rebuilt three legacy functionalities using modern methods.
    \item Contributed 90 crucial changes to the Facebook codebase.
    \item Early contract termination due to changes in project scope.
\end{itemize}
\vspace{1.0mm}

\experienceentry{Credit Agricole Corporate and Investment Bank}{Software Engineer, Contracted by Adecco Personnel, SG}{2022 May - 2023 March}{Singapore}

\begin{itemize}
    \item Maintained and rebuilt the corporate website using NextJS and Drupal 9, improving performance and accessibility.
    \item Implemented an automated deployment process for internal portals using Jenkins, saving build time.
    \item Applied data science methodologies to address data issues on the corporate website.
\end{itemize}
\vspace{1.0mm}

\experienceentry{QBurst Technologies}{Lead Engineer}{2020 August - 2022 May}{India}

\begin{itemize}
    \item Led a team of six developers, demonstrating strong leadership and management skills.
    \item Developed a web portal with a progressive web app using ReactJS, incorporating custom maps.
    \item Automated builds for Drupal and ReactJS using Acquia pipelines and Jenkins.
    \item Conducted interviews, provided project estimations, and handled other managerial tasks.
\end{itemize}

\experienceentry{Accenture}{Lead Engineer}{2018 January - 2020 August}{SG}
\begin{itemize}
    \item Subject Matter Expert in Drupal CMS.
    \item Implemented a Drupal 8 website and associated APIs.
    \item Improved load times by 1.8x with Redis cache implementation.
    \item Learned ReactJS and maintained both the website and mobile application.
    \item Engaged with clients to gather requirements, provide estimations, and plan solutions.
    \item Provided mentorship to junior developers.
\end{itemize}
\experienceentry{Axelerant Technologies}{Software Engineer}{2016 July - 2017 September}{India}
\experienceentry{Zyxware Technologies}{Senior Software Engineer}{2014 August - 2016 July}{India}
\experienceentry{Hello Infinity Business Solutions}{Co-Founder \& Technical Lead}{2012 June - 2014 August}{India}

\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}
\section{SUMMARY}
With 12 years of experience in software engineering, I specialise in complex web app development and building scalable infrastructure for millions of users. I have led teams and worked solo. I am seeking full stack web development roles.

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Back End & PHP, Python, Drupal, APIs \\
Front End & React.Js, NextJS, Tailwind, GraphQL, Typescript, Flow \\
DBMS & MySQL, PostgreSQL \\
OS & Linux, macOS \\
DevOps & Docker, Jenkins \\
Cloud & AWS, Acquia Cloud, Platform.sh 
\end{tabularx}

\section{EDUCATION}
\educationentry{B.Tech - Computer Science \& Engineering}{University of Kerala}{}

\vspace{2.0mm}
\educationentry{Micromasters - Statistics and DataScience}{MITx}{}

\section{CERTIFICATIONS}
\scoreentry{Acquia Certified Drupal 8}{}
\scoreentry{AWS Certified Cloud Practiciioner}{}
\scoreentry{Datacamp certifications}{}

\section{OPENSOURCE}
\begin{itemize}
    \item github.com/anishsheela
    \item drupal.org/u/anish.a
    \item Language Computing
    \item Conference Speaker
\end{itemize}

\section{LANGUAGES}
\begin{itemize}
    \item Malayalam (Native)
    \item English (Advanced)
    \item Tamil (Intermediate)
    \item Hindi (Basic)
    \item French (Basic)
\end{itemize}
\end{minipage}

\end{document}
